### 2015-04-07 Response/response-1.tex

Most sections of this paper are well written. The results and algorithms also seem valid. However, the motivation of minimizing the total user queue deviations is not well justified. The convergence results of some algorithms are not clearly presented. The presentation of the distributed solutions needs significant improvement. Analysis and comparison of the signaling overhead and computational complexity between the centralized and distributed algorithms are also necessary to justify the advantages of distributed algorithms.

\vspace{0.1in}
\review{We thank the reviewer for providing valuable and insightful comments.}

\begin{enumerate}
\cmnt{1} In Section II.B, please provides more justifications for the problem formulation in (6). For example, the Queue weighted sum rate maximization (Q-WSRM) is throughput optimal, i.e., if there exists a scheme which can make all queues stable, then the Q-WSRM can also do this. How about the proposed formulation in (6)? Is it also throughput optimal?

\resp \review{We thank the reviewer for the comment. 
	\begin{enumerate}
		\item The reformulation for the problem defined in (6) is required, since the SINR expression in (2) cannot be handled directly in the problem. Note that the equality constraint imposed by the SINR expression in (2) is handled by two explicit inequality constraints (16b) and (16c), leading to an approximation for the original problem in (6). We have provided justifications for the problem formulation in (6) and (16) in the paragraph before (16).
		\item The Q-WSRM scheme and the proposed schemes are all throughput optimal. It can be seen that the proposed extension Q-WSRME and the JSFRA formulations aim at minimizing the number of backlogged packets in addition to avoiding the over allocation of available resources. The JSFRA formulation using \me{\ell_1} norm as the objective minimizes the number of backlogged packets in a greedy manner at each time instant. By increasing the exponent \me{q \rightarrow \infty}, we obtain fair allocation at every transmission instant. We have included the discussions on the average of number of backlogged packets after each transmission instant for different arrival rates in Section V-C. 
		\item The equivalence between the Q-WSRM scheme and the \me{\ell_2} norm objective in the JSFRA formulation can be seen when the queue size increases. We have clarified this point in the revised manuscript. Please refer to the first paragraph in Section III-B.
	\end{enumerate}
		}

@@

\resp \review{	\begin{enumerate}
		\item In the previous manuscript, we primarily focused on evaluating the performance of all schemes by comparing the total number of backlogged packets retained in the system after each transmission instant. Since the delay is proportional to the average number of backlogged packets in the system, this implies that the delay performance was indirectly evaluated in the previous manuscript. In addition, the average delay of a particular user can be reduced by controlling the priority factor \me{a_k} in (6a), which alters the resources allocated to a particular user. We have included this statement in the manuscript in Section II-B after (6). We can also control the delay by changing the exponent used in the objective \me{\ell_q} of the JSFRA problem as discussed in bullet points before Section III.
		\item We considered the residual number of backlogged packets as a performance measure, since we assume only the instantaneous channel state informations and together with the number of backlogged packets, resources can be allocated only for a given instant.
		\item We agree with the reviewer that the delay should be compared directly to justify the advantages of the proposed schemes. In this regard, we have included a new figure to clarify this point. Please refer to Fig. 4 and the associated text in Section V-C. As can be seen, the proposed methods outperforms the existing schemes.
	\end{enumerate}
	}

\cmnt{3} In Section III.B, the convergence conditions under Algorithm 1 are not clear. First, you should be more specific about what is the SCA subproblem. Do you mean problem (19)? Second, does the uniqueness of the transmit and receive beamformers mean that the solution of the original problem in (16) is unique, or the solutions of the subproblems in (19) and (20) are unique, respectively?

\resp \review {	\begin{enumerate}
	\item We thank the reviewer for the comment. The convergence analysis has been clearly rewritten in Appendix A on the supplementary document. The discussions are provided for the convergence of the iterative Algorithm 1, \textit{i.e}, the  problem defined in (16). 
	\item The uniqueness of the convex subproblem (20) can be guaranteed by the linear constraint (19), if the initial feasible operating point is matched, \textit{i.e}, \me{q_{l,k,n} = \Im \{ \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}\} = 0} while starting the iterative solution. On the other hand, the constraint in (16b) is not unique, since the precoder is inside the absolute value operator. Once the algorithm finds a unique set of transmit precoders, all unitary rotations are also valid for the original problem in (16). The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix A-C on the supplementary document.
	\item The solution for the problem (16) is not unique, since all unitary transformations on the precoders identified by the iterative algorithm (20) are indeed the solutions for (16). 
	\item The uniqueness of the transmit precoders can be guaranteed by adding a strongly convex function in the objective as discussed in Appendix A-C on the supplementary document.
	\end{enumerate}
}

@@

\cmnt{7} The convergence analysis of the distributed algorithms is not clear. For example, what is the exact condition to ensure the convergence of the distributed algorithms. Does the distributed algorithms also converge to a stationary point?

\resp \review{We have updated the manuscript to include the discussions on the convergence of the distributed algorithm in Appendix B. The distributed algorithm attains the same stationary point as that of the centralized algorithm if we let the inner loop in Algorithm 2 to converge, \textit{i.e}, the dual or the coupling variables are updated until convergence.}

@@

\cmnt{8} I’m totally confused with the ADMM approach in Section IV.A. Many notations, such as the local interference vector and consensus interference vector are used without formal definition. What is the difference between the local interference vector and consensus interference vector? What are their relationships with the actual interference vector. It seems that you are using the same notation for all of these interference vectors and I can’t tell when a notation refers to a local interference vector, a consensus interference vector, or the actual interference vector. These questions should be clarified and perhaps you should choose the notation system more carefully. For example, in (36), there are 3 similar notations and I don’t know which one is local interference vector and which one is the actual interference vector.

\resp \review{
	\begin{enumerate}
		\item We have defined all the variables mentioned by the reviewer in the revised manuscript on Section VI-B
		\item Since the coupling between the distributed precoder designs are the interference between the BSs and the users, in the ADMM approach, the interference is treated as a local variable, which is then included in the precoder design problem for each coordinating BS. This is treated as a local variable for a specific BS. Note that the local variable is an assumption made by the BS on the actual interference caused by the neighboring BSs. Since the actual interference caused is different, the consensus has to be made between the local interference variable maintained at each BS with the global consensus interference variable, which is nothing but the average between the corresponding BSs interference. These discussions have been made in the revised manuscript in Section IV-B. For further details we have also referred the interested reader to [11], which discusses exclusively about the ADMM approach.
		\item We have revised the manuscript to avoid the subscript confusions in the ADMM approach. 
	\end{enumerate}}

### 2015-04-07 Response/response-3.tex

\cmnt{3} The solution in (21) is obtained for MMSE, i.e. for 2-norm(q=2). If \me{q=1} or \me{q=\infty}, it is actually an equivalent linear programming problem. Details for this solution should be provided.

\resp \review{We thank the reviewer for the critical comment. Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function. The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which indeed depend on the value of the exponent \me{q} used in \me{\ell_q} norm. We have modified the text to include this information on the sentence following after (22).}

\cmnt{4} The convergence proof need to be rigorous. The inequality of (23a) is opposite to the reference [28]. Also the statement on uniqueness of the transmit and the receive beamformers are not correct. Although we can choose one antenna to be real value, this does not mean the problem has unique solution!

\resp \review{\begin{enumerate}
	\item We thank the reviewer for the comment. Rigorous convergence proof for the proposed algorithm is provided in Appendix A on the supplementary document. 	
	\item The uniqueness is justified implicitly by the MSE relation in (26c) for the MSE reformulation in (28), which makes the transmit precoders to be susceptible to the phase rotation. In general, the uniqueness of the beamformer can be guaranteed by adding a strongly convex term in the objective as discussed in Appendix A-C.
\end{enumerate}}

### 2015-04-07 Response/response-4.tex

\resp \review{We agree that the original manuscript lacks the convergence proof for the JSFRA approach. We have presented a rigorous convergence proof for the proposed algorithm in Appendix A on the supplementary document. We are grateful to the reviewer for bringing our attention to reference [A] which has been cited as [32] in the revised manuscript. Some of the arguments in [32] are indeed useful to prove the convergence of the proposed algorithms in our paper.}

\cmnt{2} {Second, the optimization problems formulated only depend on $Q_k$, the current levels of backlogged packets, and not on the arrival rates. This is due to how the conditional Lyapunov drift is minimized. This approach completely removes the queue dynamics from the optimization problem, essentially leading to greedy one-shot optimization in every time instant. The framework would be more interesting if some sort of optimization (or tracking) is performed over several time instants, rather than the one-shot approach that is currently used for the JSFRA algorithms. Possibly, some expectation over the queues would be optimized then. Even if no analytical treatment of the tracking over several time-steps is added, I would at least highly recommend adding some simulation results where the proposed one-shot algorithms are performed sequentially over several time instants.}

\resp \review{
	\begin{enumerate}
	\item We thank the reviewer for the suggestion. In this paper, we proposed the precoder design to minimize the number of backlogged packets in the system at a given time. Since 
	the objective is minimized in each time instant, it somehow minimizes the objective on an average as well.
	\item We focused on the design of the precoders based on the current knowledge of the channel state information in the system model. 
	\item As suggested by the reviewer, in order to justify the gains over multiple time instants, we have now included Section V-C with Fig. 4 to compare the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots. 
	\item Fig. 4(a) demonstrate the performance of the proposed schemes and the existing algorithms using the average of the number of backlogged packets after each transmission instant for different arrival rates. The y-axis denotes the expectation taken over the number of queued packets in the system after each transmission slot.
	\item Fig. 4(b) shows the instantaneous number of backlogged packets of various schemes at each transmission instant. In Fig. 4(b), y-axis shows the total number of backlogged packets in the system after each transmission instant for an average arrival rate of \me{6} bits for all users. The x-axis represents the transmission slot at which the backlogged packets are evaluated.
	\end{enumerate}
}

@@

\cmnts{h} - {(16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).}

\resp \review{We have updated the manuscript with the explicit power constraint in (16d) as
\begin{equation}
\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b
\end{equation}}

\cmnts{i} - {p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).}

\resp \review{We thank the reviewer for the comment. We have included the text on proving the NP-hardness of the problem (16). Since the formulation in (16) can be reformulated as a \ac{WSRM} problem, which is known to be NP-hard [23], therefore, it also belongs to the class of NP-hard problems. This information is included in the third paragraph in Section III-B.}

@@

\cmnts{m} - {p. 6, col. 1, row 9: You might want to add somewhere that (22b) can be used instead of the fixed-point of (21b), since the scaling of the receive filters do not matter in the SINRs. However, does it affect the convergence of the algorithm?}

\resp \review{We thank the reviewer for the comment. We have updated the manuscript to include this discussion in the sentences following (23). The performance remains the same and the convergence behavior is not affected by this scaling, which can be seen from Fig. 1, which compares the queue deviation objective convergence using the optimal and the MMSE receiver for the JSFRA scheme with \me{\ell_1} norm.}

\cmnts{n} - {p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?}

\resp \review{To solve the nonconvex problem (16), we linearize the DC constraint (16b) around a fixed operating point. Since the operating point is a solution from the earlier iteration, it is also included in the current feasible set. Therefore, at each iteration, the algorithm finds a better solution or the same as compared to the previous solution, which leads to a monotonically decreasing objective. Please refer to Appendix A on the supplementary document for more details on the convergence analysis of the centralized algorithm.}

@@

\cmnts{o} - {p. 7, col. 1, row 35: Just because a problem is convex does not mean that it has a unique solution. (Although it seems to me that (26) should have a unique solution.) Is the problem in (26) strictly convex?}

\resp \review{
	\begin{enumerate}
		\item We thank the reviewer for the important comment and the suggestion. It is true that the convex problem need not require a unique solution in general. 
		\item The uniqueness of the beamformers for the MSE reformulation in (28) is guaranteed due to the MSE constraint (26c), which is susceptible to the transmit beamformer phase rotations.
		\item On the other hand, the uniqueness of the beamformers for the SCA approach in (20) cannot be guaranteed unless the imaginary part of \me{q_{l,k,n} = \Im \{ \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}\} = 0}. It can be achieved by using the MMSE receiver for a randomly chosen initial transmit beamformer. 
		\item The solution is not unique when the objective is zero even for a single BS. In this case, we can regularize the objective with a strictly convex term as
		\begin{equation}
		\|\tilde{\mbf{v}} \|_q + c \, \|\mbf{x} - \mbf{x}^{(i)}\|^2
		\end{equation}
		where \me{\mbf{x}} denotes the stacked vector of optimization variables and \me{\mbf{x}^{(i)}} denotes the value of \me{\mbf{x}} in the \me{\ith{i}} iteration. It has been discussed in the Appendix A-C. It makes the objective strictly convex, therefore, the resulting subproblem has a unique minimizer.
	\end{enumerate}
		}

### 2015-04-07 Response/additions.tex
adhithya-sleeping

\begin{enumerate}
\item We have provided additional information to improve the continuity in the algorithm formulation from the SINR expression as suggested by the reviewers.
\item We have included the discussion for the MSE based reformulation for different norms in the objective function.
\item We have rewritten the reduced complexity spatial resource allocation (SRA) in Section III-D for better readability.
\item We have shortened the ADMM approach as suggested by the reviewers in Section IV-B.
\item Rigorous convergence analysis is provided for the centralized algorithm in Appendix B.
\item We have included Section V-C on the queue behavior over multiple time instants. We have added Fig. 4 to show the performance of the proposed scheme over the existing precoder design algorithms.
\item We have addressed the issues in the citations and also provided additional references to prove the convergence of the centralized algorithm as suggested by the reviewers.
\end{enumerate}

Due to the page limitation imposed on the resubmitted manuscript, we have included all the Appendices as a supplementary document in the manuscript central. In what follows, the comments are listed, each followed by the corresponding reply from the authors. Unless stated explicitly, all the numbered items (figures, equations, references, citations, etc.) in the response letter refer to the revised manuscript.

>>>>

\begin{enumerate}
\item We have provided additional information to improve the continuity in the algorithm formulation from the SINR expression as suggested by the reviewers.
\item We have included the discussion for the MSE based reformulation for different norms in the objective function.
\item We have rewritten the reduced complexity spatial resource allocation (SRA) in Section III-D for better readability.
\item We have shortened the ADMM approach as suggested by the reviewers in Section IV-B.
\item Rigorous convergence analysis is provided for the centralized algorithm in Appendix A.
\item We have included Section V-C on the queue behavior over multiple time instants. We have added Fig. 4 to show the performance of the proposed scheme over the existing precoder design algorithms.
\item We have addressed the issues in the citations and also provided additional references to prove the convergence of the centralized algorithm as suggested by the reviewers.
\end{enumerate}

Due to the page limitation imposed on the resubmitted manuscript, we have included all the Appendices as a supplementary document in the manuscript central. In what follows, the comments are listed, each followed by the corresponding reply from the authors. Unless otherwise stated, all the numbered items (figures, equations, references, citations, etc) in this response letter refer to the revised manuscript.
